Fivebranes

### 2022-03-11 fivebranes/index.tex

\begin{lem}
  As $\Z/2$-graded vector spaces, we have that \[H^{\bu}\left ( \Obs_{M5}(0))=\Sym (\Pi V_{\gamma}\oplus  V_{\mu})\] where
  \begin{itemize}
    \item $V_{\gamma}$ is spanned by
          \begin{align}
            & \delta^{(0,b,c)}w_{1}^{k}w_{2}^{l}dz_{1} \\
            & \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}dz_{2}, \ \ \
             \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}dz_{3} \\
            & \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}dw_{1}, \ \ \
            \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}dw_{2}
          \end{align}

@@

The index we compute will have four fugacities, which we label as follows:
\begin{itemize}
  \item $t_{1}, t_{2}$ denote generators for the cartan of $\SU(3)$ which acts on $\C^{3}_{z}$.
  \item $r$ denotes a generator for the cartan of a $\SU(2)$ rotating the normal directions $\C^{2}_{w}$
  \item $q$ denotes a generator for the cartan of an additional $U(1)$ acting on $\C^{5}$ preserving the volume form
\end{itemize}

@@

>>>>

\begin{lem}
  As $\Z/2$-graded vector spaces, we have that \[H^{\bu}\left ( \Obs_{M5}(0)\right )=\Sym (\Pi V_{\gamma}\oplus  V_{\mu})\] where
  \begin{itemize}
    \item $V_{\gamma}$ is spanned by
          \begin{align}
            & \delta^{(0,b,c)}w_{1}^{k}w_{2}^{l}dz_{1} \\
            & \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}dz_{2}, \ \ \
             \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}dz_{3} \\
            & \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}dw_{1}, \ \ \
            \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}dw_{2}
          \end{align}

@@

The index we compute will have four fugacities, which we label as follows:
\begin{itemize}
  \item $t_{1}, t_{2}$ denote generators for the cartan of $\SU(3)$ which acts on $\C^{3}_{z}$.
  \item $q$ denotes a generator for the cartan of a $\SU(2)$ rotating the normal directions $\C^{2}_{w}$
  \item $r$ denotes a generator for the cartan of an additional $U(1)$ acting on $\C^{5}$ preserving the volume form
\end{itemize}

@@

\begin{prop}
  The $\SU(3)\times \SU(2)\times U(1)$ character of the large $N$ local operators of the M5 brane theory is given by

  \[ \operatorname{PExp} \left (\frac{q^{3}\left (\begin{aligned} & t_{1}^{-1}r+t_{1}t_{2}^{-1}r+t_{2}r+q^{-1}r^{-3/2}+qr^{-3/2} \\  - & t_{1}r^{-1}-t_{1}^{-1}t_{2}r^{-1}-t_{2}^{-1}r^{-1}-qr^{3/2}-q^{-1}r^{-3/2}
          \end{aligned}\right)}{(1-t_{1}^{-1}r)(1-t_{2}r)(1-t_{1}t_{2}^{-1}q)(1-r^{3/2}q)(1-r^{3/2}q^{-1})}\right ).\]
  \end{prop}
